Beyond ``Horizontal'' and ``Vertical'':\\ The Welfare Effects of Complex Integration\tnoteref{t1}

### 2024-08-09 doc/VerticalArrangements.tex
minor edits to figure labels. Fixed color-ordering of bars in compareplor so that pre-merger is first.

\begin{figure}
\centering
\caption{The sensitivity of consumer welfare in the Republic/Santek simulations to changes in the nesting parameter.`Integrated' assumes that all vertically integrated products are in a single nest, while `Landfill` assumes that all collectors that use the same landfill are in a single nest. A nesting parameter of 0 displays baseline results. }
\includegraphics{output/trashnest.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashNest}
\end{figure}

>>>>

\begin{figure}
\centering
\caption{The sensitivity of consumer welfare in the Republic/Santek simulations to changes in the nesting parameter.`Integrated' assumes that all vertically integrated products are in a single nest, while `Landfill' assumes that all collectors that use the same landfill are in a single nest. A nesting parameter of 0 displays baseline results. }
\includegraphics{output/trashnest.png}\\
\footnotesize{Notes: ``WasteConn'' stands for Waste Connections.}
\label{fig:TrashNest}
\end{figure}
